Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-07 article/article.Rmd
Commit 2024-06-07 14:14

An important aspect of the variability of solar radiation is its interaction with the
clouds. In general, clouds can attenuate a fraction  of solar irradiance, but under
certain conditions, can lead to  enhancement of the global horizontal irradiance
(GHI) reaching the ground. This effect can locally increase the observed GHI to
levels even higher than the expected clear-sky irradiance [@Cordero2023; @Vamvakas2020 see references therein].

>>>>

An important aspect of the variability of solar radiation is its interaction with the
clouds. In general, clouds can attenuate a fraction  of solar irradiance, but under
certain conditions, can lead to  enhancement of the global horizontal irradiance
(GHI) reaching the ground. This effect can locally increase the observed GHI to
levels even higher than the expected clear-sky irradiance [see references therein].
